---
title: "R data frames exercises"
author: "Alex Monteil"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

\textbf{1) Recreate the dataframe by creating vectors first}\

```{r}
age <- c(22, 25, 26)
weight <- c(150, 165, 120)
sex <- c("M", "M", "F")
df <- data.frame(age, weight, sex)
rownames(df) <- c("Sam", "Frank", "Amy")
print(df)
```

\textbf{2) Check is mtcars is a data frame}\

```{r}
is.data.frame(mtcars)
```

\textbf{3) Convert the matrix into a data frame}\

```{r}
mat <- matrix(1:25, nrow = 5)
df2 <- as.data.frame(mat)
print(df2)
```

\textbf{4) Set the mtcars built in data frame in a df\_cars variable}\

```{r}
df_cars <- mtcars
```

\textbf{5) Display the first 6 rows of df\_cars}\

```{r}
head(df_cars)
```

\textbf{6) What is the average mpg value for all cars ?}\

```{r}
mean(df_cars$mpg)
```
\textbf{7) Select cars that have 6 cylinders}\

```{r}
subset(df_cars, subset = cyl == 6)
```

\textbf{8) Select columns am, gear and carb}\

```{r}
df_cars[,c("am", "gear", "carb")]
```

\textbf{9) Create a new column called performance which is calculated as hp divided by wt}\

```{r}
df_cars$performance <- df_cars$hp/df_cars$wt
head(df_cars)
```

\textbf{10) Your performance column will have several decimal precision. Figure out how to use round to reduce it to 2 decimal places}\

```{r}
df_cars$performance <- round(df_cars$performance, digits = 2)
head(df_cars)
```

\textbf{11) What is the mpg of the Hornet Sportabout ?}\

```{r}
df_cars["Hornet Sportabout", "mpg"]
```

