---
title: "R Basics Exercises"
author: "Alex Monteil"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\textbf{1) What is 2 to the power of 5 ?}\

```{r}
2^5
```

\textbf{2) Create a vector called stock prices with the following data points: 23,27,23,21,34}\

```{r}
stock_prices <- c(23,27,23,21,34)
stock_prices
```

\textbf{3) Assign names to the price data points relating to the day of the week, starting with Mon, Tue, Wed, etc ...}\

```{r}
names(stock_prices) <- c("Mon", "Tue", "Wed", "Thu", "Fri")
stock_prices
```
\textbf{4) What is the average of the stock price for the week ?}\

```{r}
mean(stock_prices)
```
\textbf{5) Create a vector called over_23 consisting of logicals that correspond to the days where the stock price was more than $23}\

```{r}
over_23 <- stock_prices > 23
over_23
```
\textbf{6) Use the over\_23 vector to filter out the sock\_prices vector only return the elements over \$23}\

```{r}
stock_prices[over_23]
```
\textbf{7) Use a built in function to find the day the price was the highest}\

```{r}
stock_prices[which.max(stock_prices)]
```

