---
title: "R Matrices Exercices"
author: "Alex Monteil"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\textbf{Create 2 vectors A and B where A is (1,2,3) and B is (4,5,6) and create a 2 by 3 matrix from the vectors such that each vector is a row}\

```{r}
A <- 1:3
B <- 4:6
combined_data <- c(A,B)
mat1 <- matrix(data = combined_data, nrow = 2, byrow = T)
print(mat1)
```

\textbf{Create a 3 by 3 matrix consisting of the numbers 1 through 9 using 1:9 directly. Row 1 (1,2,3) Row 2 (4,5,6) Row 3 (7,8,9)}\

```{r}
mat2 <- matrix(data = 1:9, nrow = 3, byrow = T)
print(mat2)
```

\textbf{Confirm that mat2 is a matrix}\

```{r}
is.matrix(mat2)
```

\textbf{Create a 5 by 5 matrix consisting of the numbers 1-25 and assign it to mat3. Top row should be 1-5}\

```{r}
mat3 <- matrix(data = 1:25, nrow = 5, byrow = T)
print(mat3)
```

\textbf{Select the submatrix [[7,8], [12,13]]}\

```{r}
mat3[2:3, 2:3]
```

\textbf{Select the submatrix [[19,20], [24,25]]}\

```{r}
mat3[4:5, 4:5]
```

\textbf{Find out how to use runif() to create a 4 by 5 matrix consisting of 20 random numbers}\

```{r}
help(runif)
mat_random <- matrix(data = runif(20, 0, 100), nrow = 4)
print(mat_random)
```

