---
title: "R - Data Wrangling Exercises"
author: "Alex Monteil"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(dplyr)
```


\textbf{1) Using the built in mtcars data frame, return rows that have an mpg value greater than 20 and that have 6 cylinders}\


```{r}
filter(mtcars, mpg > 20, cyl == 6)
```

\textbf{2) Reorder the data frame by cyl first then descending wt}\

```{r}
arrange(mtcars, cyl, desc(wt))
```

\textbf{3) Select columns mpg and hp}\

```{r}
select(mtcars, mpg, hp)
```

\textbf{4) Select the unique values of the gear column}\

```{r}
distinct(select(mtcars, gear))
```

\textbf{5) Create a new column called performance which is calculated as: hp divided by wt}\

```{r}
mutate(mtcars, Performance = hp / wt)
```

\textbf{6) Find mean mpg value using dplyr}\

```{r}
summarise(mtcars, avg_mpg = mean(mpg, na.rm = T))
```
\textbf{7) Use pipe operators to get the mean hp value for cars with 6 cylinders}\

```{r}
mtcars %>% 
  filter(cyl == 6) %>%
  summarise(avg_hp = mean(hp, na.rm = T))
```

